Automatically drawing vegetation classification maps using digital time-lapse cameras in alpine ecosystems

### 2022-10-30 paper/paper.Rmd
modified paper

---
title: Automatically drawing vegetation maps using digital time-lapse cameras in alpine ecosystems
authors:
  - name: Ryotaro Okamoto
    thanks: https://github.com/0kam
    department: Doctoral Program in Biology
    affiliation: University of Tsukuba
    location: 1-1-1 Tennodai, Tsukuba, Ibaraki 305-8577 Japan. 
    email: okamoto.ryotaro.su@alumni.tsukuba.ac.jp
  - name: Hiroyuki Oguma
    department: Biodiversity Division
    affiliation: National Institute for Environmental Studies
    location: 16-2 Onogawa, Tsukuba, Ibaraki 305-8506 Japan
    email: oguma@nies.go.jp
  - name: Reiko Ide
    department: Earth System Division
    affiliation: National Institute for Environmental Studies
    location: 16-2 Onogawa, Tsukuba, Ibaraki 305-8506 Japan
    email: ide.reiko@nies.go.jp
abstract: |
  Alpine ecosystems are particularly vulnerable to the effect of climate change. Monitoring the distribution of alpine vegetation is required to plan practical conservation activities. However, conventional field observation and satellite remote sensing have difficulties in the coverage and frequency in alpine areas. Researchers have also utilized ground-based time-lapse cameras to observe alpine regions' snowmelt and vegetation phenology. Such time-lapse cameras have significant advantages in cost, resolution, and frequency. However, no research has used these to monitor the vegetation distribution. This study proposes a novel method to draw georeferenced vegetation maps from ground-based imagery of the Japanese alps. Our approach has two components: the classification and georectification method. The proposed classification method uses pixel time series acquired from autumn images to utilize the patterns of autumn foliage. We show that using time-lapse imagery and a Recurrent Neural Network improves the performance of the vegetation classification. We also developed a novel method to accurately transform a ground-based image into georeferenced data. We propose 1. an automated procedure to acquire Ground Control Points (GCPs) and 2. a camera model that considers the lens distortion for accurate georectification. We show that our approach outperforms the conventional method. The proposed method achieved sufficient accuracy to observe the vegetation distribution on a plant-community scale. The evaluation reveals an F1 score of 0.937 in the vegetation classification and a root mean square error (RMSE) of 3.4 m in the georectification. Our results highlight the potential of cheap time-lapse cameras to monitor the distribution of alpine vegetation. The proposed method should significantly contribute to effective conservation planning of the alpine ecosystems.
keywords:
  - alpine ecology
  - deep learning
  - ecosystem monitoring
bibliography: export.bib
biblio-style: unsrt
output:
  bookdown::pdf_book:
    fig_caption: yes
    base_format: rticles::arxiv_article

header-includes:
  - \usepackage{amsmath}
  - \setlength{\parindent}{10.5pt}
---

```{r setup, include=FALSE}
library(tidyverse)
library(magrittr)
library(kableExtra)
library(tidyverse)
library(magrittr)
library(fs)
library(lubridate)
```

@@

The effects of climate change on terrestrial ecosystems are particularly significant in alpine regions (\cite{IPCC2007}). Alpine vegetation depends on severe conditions such as low temperatures and long snow-covered periods. Thus alpine areas have rare and unique species adapted to the extreme environments. Several studies have reported that recent global climatic changes, e.g., increasing temperatures and reducing snow-covered periods, have accelerated the invasion of non-native species into alpine areas (see \cite{Alexander2016AlpBotany}). In Japan, dwarf bamboo (*Sasa kurilensis*) has invaded alpine snow meadows, probably driven by the extension of the snow-free period (\cite{Kudo2011EcoEvo}). Also, climate change has affected the growth and phenologies of native species. For example, the growth of dwarf pine (*Pinus pumila*), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}). Effective conservation planning requires constant monitoring of vegetation distribution to detect such changes. Also, since the impact of climate change on alpine vegetation varies depending on species and the microhabitats (\cite{Kudo2010AAA}), spatially high-resolution monitoring with a wide range is required.

Previous studies have mainly depended on field observations, yet it is hard to cover broad areas in alpine regions due to the poor accessibility and severe weather. Satellite, airborne, and Unmanned Aerial Vehicle (UAV) remote sensing methods are alternatives. However, satellite imagery of alpine areas is rarely available due to cloud cover, and the spatial resolution is not enough to observe vegetation changes at the plant community scale. Airborne imagery can obtain high-resolution data, but its cost becomes a bottleneck for frequent monitoring. Although UAV methods have become a cost-effective tool for ecological monitoring (\cite{Baena2017PLOSONE}), operating UAVs in alpine regions is challenging due to the strong wind and harsh topology.

On the other hand, researchers have also utilized automated digital time-lapse cameras mounted on the ground for monitoring green-leaf phenologies in forests (\cite{Richardson2009EcolAppl}), grasslands (\cite{Browning2017RemSen}), and alpine meadows (\cite{IdeOguma2013EcolInfom}). Unlike satellite imagery, ground-based cameras provide images free of clouds and atmospheric effects. Also, they can obtain high-resolution (i.e., sub-meter scale) and frequent (i.e., daily or hourly) images at a meager cost. These studies set some regions of interest (ROI) in the images and calculate the phenology index (e.g., excess greenness, \cite{Woebbecke1995ASAE}). However, few studies have utilized such images in monitoring vegetation distributions. This lack of studies seems to be because applying such time-lapse imagery in monitoring vegetation distribution has two technical challenges.

First, unlike satellites' multispectral sensors, ordinal digital cameras can only obtain three bands (Red, Green, and Blue), making it harder to classify the vegetation. Second, since digital time-lapse cameras are mounted on the ground, transforming these images into geospatial data (e.g., orthoimage) is challenging. In other words, even if we classify the vegetation from such images, we cannot quantitatively measure and analyze it as geographic data. It is essential to treat ground-based images as geographic data to utilize them in conservation planning.

This study proposes an automated method for drawing vegetation maps with a digital time-lapse camera by solving these two challenges. We solved the first challenge by using time-lapse images to classify vegetation. Since the autumn leaf phenology varies among species, we utilized that information. We show the effectiveness of such phenological information in vegetation classification. We also developed a novel method for transforming a ground-based photograph into geographic data to tackle the second challenge. Finally, we show an example of a vegetation map drawn by the proposed method. We aim to use cheap but powerful digital time-lapse cameras in alpine ecosystem monitoring and conservation.

@@

## Digital time-lapse camera imagery

We used time-lapse images of a Japanese alpine region owned by the National Institute for Environmental Studies, Japan (NIES). All the images are publically available on NIES' webpage (https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2). In 2010, NIES installed the digital time-lapse camera (EOS 5D MK2, Canon Inc., 21 M pixels) on a mountain lodge Murodo-sanso (about 2350 m a.s.l., above the forest limit), located at the foot of Mt. Tateyama (3015 m a.s.l.), in the Nothern Japanese Alps (Fig. \ref{fig:map}). The camera takes a photograph per hour, from 6 a.m. to 7 p.m. . The camera's field of view (FOV) includes Mt. Tateyama, which ranges from about 2350 m a.s.l. to 3015 m a.s.l. in elevation. The area has a complex mosaic-like vegetation structure because of its topography, including rocks, cliffs, curls, and moraines. From April to November, the camera observed the snowmelt and seasonal phenology of evergreen(e.g., *Pinus pumila*) and deciduous (*Sorbus* sp.,  *Betula ermanii*) dwarf trees, dwarf bamboos (e.g., *Sasa kurilensis*), and alpine shrubs and herbaceous plants (e.g., *Geum pentapetalum*, *Nephrophyllidium crista-galli*). This study used images from the summer and fall of 2015 to classify vegetation with the temporal patterns of the leaf color.

@@

### Selecting images

First, we selected images. We choose seven days with good weather from late summer to late fall of 2015 (8/25, 9/5, 9/12, 9/20, 9/26, 10/3, 10/10). The temporal patterns of autumn foliage coloration are largely different among species (see Fig. \ref{fig:pixtimeseries}). Our method utilizes this information in the vegetation classification. Time-lapse cameras are particularly good at observing such temporal changes of the vegetation, while UAVs and airborne imagery cost much.

>>>>

---
title: Automatically drawing vegetation classification maps using digital time-lapse cameras in alpine ecosystems
authors:
  - name: Ryotaro Okamoto
    thanks: https://github.com/0kam
    department: Doctoral Program in Biology
    affiliation: University of Tsukuba
    location: 1-1-1 Tennodai, Tsukuba, Ibaraki 305-8577 Japan. 
    email: okamoto.ryotaro.su@alumni.tsukuba.ac.jp
  - name: Hiroyuki Oguma
    department: Biodiversity Division
    affiliation: National Institute for Environmental Studies
    location: 16-2 Onogawa, Tsukuba, Ibaraki 305-8506 Japan
    email: oguma@nies.go.jp
  - name: Reiko Ide
    department: Earth System Division
    affiliation: National Institute for Environmental Studies
    location: 16-2 Onogawa, Tsukuba, Ibaraki 305-8506 Japan
    email: ide.reiko@nies.go.jp
abstract: |
  Alpine ecosystems are particularly vulnerable to the effect of climate change. Monitoring the distribution of alpine vegetation is required to plan practical conservation activities. However, conventional field observation and satellite remote sensing have difficulties in the coverage and frequency in alpine areas. Researchers have also utilized ground-based time-lapse cameras to observe alpine regions' snowmelt and vegetation phenology. Such time-lapse cameras have significant advantages in cost, resolution, and frequency. However, no research has used these to monitor the vegetation distribution. This study proposes a novel method to draw georeferenced vegetation maps from ground-based imagery of the Japanese alps. Our approach has two components: the classification and georectification method. The proposed classification method uses pixel time series acquired from autumn images to utilize the patterns of autumn foliage. We show that using time-lapse imagery and a Recurrent Neural Network improves the performance of the vegetation classification. We also developed a novel method to accurately transform a ground-based image into georeferenced data. We propose 1. an automated procedure to acquire Ground Control Points (GCPs) and 2. a camera model that considers the lens distortion for accurate georectification. We show that our approach outperforms the conventional method. The proposed method achieved sufficient accuracy to observe the vegetation distribution on a plant-community scale. The evaluation reveals an F1 score of 0.937 in the vegetation classification and a root mean square error (RMSE) of 3.4 m in the georectification. Our results highlight the potential of cheap time-lapse cameras to monitor the distribution of alpine vegetation. The proposed method should significantly contribute to effective conservation planning of the alpine ecosystems.
keywords:
  - alpine ecology
  - deep learning
  - ecosystem monitoring
bibliography: export.bib
biblio-style: unsrt
output:
  bookdown::pdf_book:
    fig_caption: yes
    base_format: rticles::arxiv_article

header-includes:
  - \usepackage{amsmath}
  - \usepackage{nicefrac}
  - \setlength{\parindent}{10.5pt}
---

```{r setup, include=FALSE}
library(tidyverse)
library(magrittr)
library(kableExtra)
library(tidyverse)
library(magrittr)
library(fs)
library(lubridate)
setwd("~/projects/VegetationMapPaper/paper/")
```

@@

The effects of climate change on terrestrial ecosystems are particularly significant in alpine regions (\cite{IPCC2007}). Alpine vegetation depends on severe conditions such as low temperatures and long snow-covered periods. Thus alpine areas have unique species adapted to such extreme environments. Several studies have reported that recent global climatic changes, e.g., increasing temperatures and reducing snow-covered periods, have accelerated the invasion of non-native species into alpine areas (see \cite{Alexander2016AlpBotany}). In Japan, dwarf bamboo (*Sasa kurilensis*) has invaded alpine snow meadows, probably driven by the extension of the snow-free period (\cite{Kudo2011EcoEvo}). Climate change has also affected the growth and phenologies of native species. For example, the growth of dwarf pine (*Pinus pumila*), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}). In addition, researchers have reported that such changes vary depending on species and microhabitats (\cite{Kudo2010AAA}, \cite{XXXXXX}). Understanding and predicting the undergoing changes of alpine vegetation requires a monitoring method scalable to a wide range with a spatially and temporally high resolution.

Previous studies have mainly depended on field observations, yet it is hard to cover broad areas in alpine regions due to the poor accessibility and severe weather. Satellite, airborne, and Unmanned Aerial Vehicle (UAV) remote sensing methods are alternatives. However, satellite imagery of alpine areas is rarely available due to cloud cover, and the spatial resolution is not enough to observe vegetation changes at the plant community scale. Airborne imagery can obtain high-resolution data, but its cost becomes a bottleneck for frequent monitoring. Although UAV methods have become a cost-effective tool for ecological monitoring (\cite{Baena2017PLOSONE}), operating UAVs in alpine regions is sometimes challenging due to the strong wind and harsh topology.

On the other hand, researchers have also utilized automated digital time-lapse cameras mounted on the ground for monitoring green-leaf phenologies in forests (\cite{Richardson2009EcolAppl}), grasslands (\cite{Browning2017RemSen}), and alpine meadows (\cite{IdeOguma2013EcolInfom}). Unlike satellite imagery, ground-based cameras provide images free of clouds and atmospheric effects. Also, they can obtain high-resolution (i.e., sub-meter scale) and frequent (i.e., daily or hourly) images at a meager cost. Most previous studies with such cameras were about calculating the phenology index (e.g., excess greenness, \cite{Woebbecke1995ASAE}) by setting some regions of interest (ROI) in the images. Few studies have utilized such images in monitoring vegetation distributions. This lack of studies seems to be because applying such time-lapse imagery in monitoring vegetation distribution has two technical challenges.

First, unlike satellites' multispectral sensors, ordinal digital cameras can only obtain three bands (Red, Green, and Blue), making it harder to classify the vegetation. Second, since digital time-lapse cameras are mounted on the ground, transforming these images into geospatial data (e.g., orthoimage, this process is called georectification) is challenging. In other words, even if we classify the vegetation from such images, we cannot quantitatively measure and analyze it using Geographic Information Systems (GIS) tools. Georectification is essential for utilizing time-lapse cameras in scientific conservation planning.

This study proposes an automated method for drawing vegetation classification maps with a digital time-lapse camera by solving these two challenges. We solved the first challenge by using time-lapse images to classify vegetation. The autumn leaf phenology, which varies among species, was utilized in the classification process. We show the effectiveness of such phenological information in vegetation classification. A novel georectification method for ground-based photographs was also developed to tackle the second challenge. Finally, the proposed method generated a vegetation classification map from time-lapse images taken in the Japanese alps. Our method enables us to continuously monitor vegetation distribution and its changes at a plant-community scale, covering broad areas at a meager cost.

@@

Our approach has three steps:
Image-to-image alignment for correcting the movements of the camera
Vegetation classification for classifying each pixel into vegetation categories
Georectification for transforming vegetation classification results into geospatial data
Fig. \ref{fig:diagram} shows the overview of the entire process. The proposed method requires training data for the vegetation classification model, a Digital Elevation Model (DEM), and a georectified airborne/satellite image that covers the camera's field of view.

(ref:diagram) An overview of the proposed procedure

```{r, diagram, echo=FALSE, message=FALSE, fig.cap="(ref:diagram)", out.width="50%", auto_pdf = TRUE}
knitr::include_graphics("paper_files/figures/diagram.png")
```

## Time-lapse image acquisition

Our method is intended for digital time-lapse images of alpine landscapes. In this study, we used time-lapse photos of a Japanese alpine region owned by the National Institute for Environmental Studies, Japan (NIES). All the images are publically available on NIES' webpage (https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2). In 2010, NIES installed the digital time-lapse camera (EOS 5D MK2, Canon Inc., 21 M pixels) on a mountain lodge Murodo-sanso (about 2350 m a.s.l., above the forest limit), located at the foot of Mt. Tateyama (3015 m a.s.l.), in the Nothern Japanese Alps (Fig. \ref{fig:map}). The photographs were taken hourly, from 6 a.m. to 7 p.m. The camera's field of view (FOV) includes Mt. Tateyama, which ranges from about 2350 m a.s.l. to 3015 m a.s.l. in elevation. The pixel size on the ground was about 0.5 m at the ridge, about 1 km from the cameras. The area has a complex mosaic-like vegetation structure because of its topography, including rocks, cliffs, curls, and moraines. From April to November, the camera observed the snowmelt and seasonal phenology of evergreen(e.g., *Pinus pumila*) and deciduous (*Sorbus* sp.,  *Betula ermanii*) dwarf trees, dwarf bamboos (e.g., *Sasa kurilensis*), and alpine shrubs and herbaceous plants (e.g., *Geum pentapetalum*, *Nephrophyllidium crista-galli*).

@@

### Image selection
We selected seven images from late summer to late fall (8/25, 9/5, 9/12, 9/20, 9/26, 10/3, and 10/10) in 2015. Since the temporal patterns of autumn foliage coloration vary among species (see Fig. \ref{fig:pixtimeseries}), this season is suitable for classifying vegetation. While acquiring a series of images costs a lot with UAVs and airborne imagery, time-lapse cameras are particularly good at observing such temporal patterns of leaf color.

### 2022-10-30 paper/paper.tex
modified paper

\title{Automatically drawing vegetation maps using digital time-lapse cameras in alpine ecosystems}

@@

\usepackage{amsmath}
\setlength{\parindent}{10.5pt}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\begin{document}
\maketitle

@@

The effects of climate change on terrestrial ecosystems are particularly significant in alpine regions (\cite{IPCC2007}). Alpine vegetation depends on severe conditions such as low temperatures and long snow-covered periods. Thus alpine areas have rare and unique species adapted to the extreme environments. Several studies have reported that recent global climatic changes, e.g., increasing temperatures and reducing snow-covered periods, have accelerated the invasion of non-native species into alpine areas (see \cite{Alexander2016AlpBotany}). In Japan, dwarf bamboo (\emph{Sasa kurilensis}) has invaded alpine snow meadows, probably driven by the extension of the snow-free period (\cite{Kudo2011EcoEvo}). Also, climate change has affected the growth and phenologies of native species. For example, the growth of dwarf pine (\emph{Pinus pumila}), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}). Effective conservation planning requires constant monitoring of vegetation distribution to detect such changes. Also, since the impact of climate change on alpine vegetation varies depending on species and the microhabitats (\cite{Kudo2010AAA}), spatially high-resolution monitoring with a wide range is required.

Previous studies have mainly depended on field observations, yet it is hard to cover broad areas in alpine regions due to the poor accessibility and severe weather. Satellite, airborne, and Unmanned Aerial Vehicle (UAV) remote sensing methods are alternatives. However, satellite imagery of alpine areas is rarely available due to cloud cover, and the spatial resolution is not enough to observe vegetation changes at the plant community scale. Airborne imagery can obtain high-resolution data, but its cost becomes a bottleneck for frequent monitoring. Although UAV methods have become a cost-effective tool for ecological monitoring (\cite{Baena2017PLOSONE}), operating UAVs in alpine regions is challenging due to the strong wind and harsh topology.

On the other hand, researchers have also utilized automated digital time-lapse cameras mounted on the ground for monitoring green-leaf phenologies in forests (\cite{Richardson2009EcolAppl}), grasslands (\cite{Browning2017RemSen}), and alpine meadows (\cite{IdeOguma2013EcolInfom}). Unlike satellite imagery, ground-based cameras provide images free of clouds and atmospheric effects. Also, they can obtain high-resolution (i.e., sub-meter scale) and frequent (i.e., daily or hourly) images at a meager cost. These studies set some regions of interest (ROI) in the images and calculate the phenology index (e.g., excess greenness, \cite{Woebbecke1995ASAE}). However, few studies have utilized such images in monitoring vegetation distributions. This lack of studies seems to be because applying such time-lapse imagery in monitoring vegetation distribution has two technical challenges.

First, unlike satellites' multispectral sensors, ordinal digital cameras can only obtain three bands (Red, Green, and Blue), making it harder to classify the vegetation. Second, since digital time-lapse cameras are mounted on the ground, transforming these images into geospatial data (e.g., orthoimage) is challenging. In other words, even if we classify the vegetation from such images, we cannot quantitatively measure and analyze it as geographic data. It is essential to treat ground-based images as geographic data to utilize them in conservation planning.

This study proposes an automated method for drawing vegetation maps with a digital time-lapse camera by solving these two challenges. We solved the first challenge by using time-lapse images to classify vegetation. Since the autumn leaf phenology varies among species, we utilized that information. We show the effectiveness of such phenological information in vegetation classification. We also developed a novel method for transforming a ground-based photograph into geographic data to tackle the second challenge. Finally, we show an example of a vegetation map drawn by the proposed method. We aim to use cheap but powerful digital time-lapse cameras in alpine ecosystem monitoring and conservation.

@@

\hypertarget{digital-time-lapse-camera-imagery}{%
\subsection{Digital time-lapse camera imagery}\label{digital-time-lapse-camera-imagery}}

We used time-lapse images of a Japanese alpine region owned by the National Institute for Environmental Studies, Japan (NIES). All the images are publically available on NIES' webpage (\url{https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2}). In 2010, NIES installed the digital time-lapse camera (EOS 5D MK2, Canon Inc., 21 M pixels) on a mountain lodge Murodo-sanso (about 2350 m a.s.l., above the forest limit), located at the foot of Mt. Tateyama (3015 m a.s.l.), in the Nothern Japanese Alps (Fig. \ref{fig:map}). The camera takes a photograph per hour, from 6 a.m. to 7 p.m. . The camera's field of view (FOV) includes Mt. Tateyama, which ranges from about 2350 m a.s.l. to 3015 m a.s.l. in elevation. The area has a complex mosaic-like vegetation structure because of its topography, including rocks, cliffs, curls, and moraines. From April to November, the camera observed the snowmelt and seasonal phenology of evergreen(e.g., \emph{Pinus pumila}) and deciduous (\emph{Sorbus} sp., \emph{Betula ermanii}) dwarf trees, dwarf bamboos (e.g., \emph{Sasa kurilensis}), and alpine shrubs and herbaceous plants (e.g., \emph{Geum pentapetalum}, \emph{Nephrophyllidium crista-galli}). This study used images from the summer and fall of 2015 to classify vegetation with the temporal patterns of the leaf color.

@@

\hypertarget{selecting-images}{%
\subsubsection{Selecting images}\label{selecting-images}}

First, we selected images. We choose seven days with good weather from late summer to late fall of 2015 (8/25, 9/5, 9/12, 9/20, 9/26, 10/3, 10/10). The temporal patterns of autumn foliage coloration are largely different among species (see Fig. \ref{fig:pixtimeseries}). Our method utilizes this information in the vegetation classification. Time-lapse cameras are particularly good at observing such temporal changes of the vegetation, while UAVs and airborne imagery cost much.

>>>>

\title{Automatically drawing vegetation classification maps using digital time-lapse cameras in alpine ecosystems}

@@

\usepackage{amsmath}
\usepackage{nicefrac}
\setlength{\parindent}{10.5pt}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\begin{document}
\maketitle

@@

\hypertarget{introduction-1}{%
\section{Introduction}\label{introduction-1}}

The effects of climate change on terrestrial ecosystems are particularly significant in alpine regions (\cite{IPCC2007}). Alpine vegetation depends on severe conditions such as low temperatures and long snow-covered periods. Thus alpine areas have unique species adapted to such extreme environments. Several studies have reported that recent global climatic changes, e.g., increasing temperatures and reducing snow-covered periods, have accelerated the invasion of non-native species into alpine areas (see \cite{Alexander2016AlpBotany}). In Japan, dwarf bamboo (\emph{Sasa kurilensis}) has invaded alpine snow meadows, probably driven by the extension of the snow-free period (\cite{Kudo2011EcoEvo}). Climate change has also affected the growth and phenologies of native species. For example, the growth of dwarf pine (\emph{Pinus pumila}), a dominant species in Japanese alpine regions, has been affected by climatic conditions such as temperature and snowmelt (\cite{Amagai2015EcoRes}). In addition, researchers have reported that such changes vary depending on species and microhabitats (\cite{Kudo2010AAA}, \cite{XXXXXX}). Understanding and predicting the undergoing changes of alpine vegetation requires a monitoring method scalable to a wide range with a spatially and temporally high resolution.

Previous studies have mainly depended on field observations, yet it is hard to cover broad areas in alpine regions due to the poor accessibility and severe weather. Satellite, airborne, and Unmanned Aerial Vehicle (UAV) remote sensing methods are alternatives. However, satellite imagery of alpine areas is rarely available due to cloud cover, and the spatial resolution is not enough to observe vegetation changes at the plant community scale. Airborne imagery can obtain high-resolution data, but its cost becomes a bottleneck for frequent monitoring. Although UAV methods have become a cost-effective tool for ecological monitoring (\cite{Baena2017PLOSONE}), operating UAVs in alpine regions is sometimes challenging due to the strong wind and harsh topology.

On the other hand, researchers have also utilized automated digital time-lapse cameras mounted on the ground for monitoring green-leaf phenologies in forests (\cite{Richardson2009EcolAppl}), grasslands (\cite{Browning2017RemSen}), and alpine meadows (\cite{IdeOguma2013EcolInfom}). Unlike satellite imagery, ground-based cameras provide images free of clouds and atmospheric effects. Also, they can obtain high-resolution (i.e., sub-meter scale) and frequent (i.e., daily or hourly) images at a meager cost. Most previous studies with such cameras were about calculating the phenology index (e.g., excess greenness, \cite{Woebbecke1995ASAE}) by setting some regions of interest (ROI) in the images. Few studies have utilized such images in monitoring vegetation distributions. This lack of studies seems to be because applying such time-lapse imagery in monitoring vegetation distribution has two technical challenges.

First, unlike satellites' multispectral sensors, ordinal digital cameras can only obtain three bands (Red, Green, and Blue), making it harder to classify the vegetation. Second, since digital time-lapse cameras are mounted on the ground, transforming these images into geospatial data (e.g., orthoimage, this process is called georectification) is challenging. In other words, even if we classify the vegetation from such images, we cannot quantitatively measure and analyze it using Geographic Information Systems (GIS) tools. Georectification is essential for utilizing time-lapse cameras in scientific conservation planning.

This study proposes an automated method for drawing vegetation classification maps with a digital time-lapse camera by solving these two challenges. We solved the first challenge by using time-lapse images to classify vegetation. The autumn leaf phenology, which varies among species, was utilized in the classification process. We show the effectiveness of such phenological information in vegetation classification. A novel georectification method for ground-based photographs was also developed to tackle the second challenge. Finally, the proposed method generated a vegetation classification map from time-lapse images taken in the Japanese alps. Our method enables us to continuously monitor vegetation distribution and its changes at a plant-community scale, covering broad areas at a meager cost.

@@

Our approach has three steps:
Image-to-image alignment for correcting the movements of the camera
Vegetation classification for classifying each pixel into vegetation categories
Georectification for transforming vegetation classification results into geospatial data
Fig. \ref{fig:diagram} shows the overview of the entire process. The proposed method requires training data for the vegetation classification model, a Digital Elevation Model (DEM), and a georectified airborne/satellite image that covers the camera's field of view.

\begin{figure}
\includegraphics[width=0.5\linewidth]{paper_files/figures/diagram} \caption{An overview of the proposed procedure}\label{fig:diagram}
\end{figure}

\hypertarget{time-lapse-image-acquisition}{%
\subsection{Time-lapse image acquisition}\label{time-lapse-image-acquisition}}

Our method is intended for digital time-lapse images of alpine landscapes. In this study, we used time-lapse photos of a Japanese alpine region owned by the National Institute for Environmental Studies, Japan (NIES). All the images are publically available on NIES' webpage (\url{https://db.cger.nies.go.jp/gem/ja/mountain/station.html?id=2}). In 2010, NIES installed the digital time-lapse camera (EOS 5D MK2, Canon Inc., 21 M pixels) on a mountain lodge Murodo-sanso (about 2350 m a.s.l., above the forest limit), located at the foot of Mt. Tateyama (3015 m a.s.l.), in the Nothern Japanese Alps (Fig. \ref{fig:map}). The photographs were taken hourly, from 6 a.m. to 7 p.m. The camera's field of view (FOV) includes Mt. Tateyama, which ranges from about 2350 m a.s.l. to 3015 m a.s.l. in elevation. The pixel size on the ground was about 0.5 m at the ridge, about 1 km from the cameras. The area has a complex mosaic-like vegetation structure because of its topography, including rocks, cliffs, curls, and moraines. From April to November, the camera observed the snowmelt and seasonal phenology of evergreen(e.g., \emph{Pinus pumila}) and deciduous (\emph{Sorbus} sp., \emph{Betula ermanii}) dwarf trees, dwarf bamboos (e.g., \emph{Sasa kurilensis}), and alpine shrubs and herbaceous plants (e.g., \emph{Geum pentapetalum}, \emph{Nephrophyllidium crista-galli}).

@@

\hypertarget{image-selection}{%
\subsubsection{Image selection}\label{image-selection}}

We selected seven images from late summer to late fall (8/25, 9/5, 9/12, 9/20, 9/26, 10/3, and 10/10) in 2015. Since the temporal patterns of autumn foliage coloration vary among species (see Fig. \ref{fig:pixtimeseries}), this season is suitable for classifying vegetation. While acquiring a series of images costs a lot with UAVs and airborne imagery, time-lapse cameras are particularly good at observing such temporal patterns of leaf color.
